Capturing the shape of our experiences and how we remember them

### 2018-08-20 paper/main.tex
small change to discussion

To conclude, we'll revisit the question of what it means to remember something. Our view is that ``successful remembering'' is about recovering the ``trajectory'' of an experience, rather than the ability to recognize/recall any of its particular isolated details. Decades of research suggest that episodic memories are not veridical and context-free snapshots of the past, and so treating (and modelling) them as such is overly simplistic at best (and counterproductive at worst). While its undeniable that these models have been immensely useful in advancing our understanding of the fundamental principles that govern human memory, they are severely limited in their ability to explain memory for naturalistic experiences. Real-life experiences are highly structured in time, and so our experiments and models of memory should account for this fact.

>>>>

To conclude, we'll revisit the question of what it means to remember something. Our view is that ``successful remembering'' is about recovering the ``trajectory'' of an experience, rather than the ability to recognize/recall any of its particular isolated details. Decades of research suggest that episodic memories are not veridical and context-free snapshots of the past, and so treating (and modelling) them as such is overly simplistic at best (and counterproductive at worst). While its undeniable that these models have been useful in advancing our understanding of human memory, they are severely limited in their ability to explain memory for naturalistic experiences. Real-life experiences are highly structured in time, and so to have a complete understanding of the human memory system, our experiments and models of memory should not ignore this fact. This work provides a methodological and theoretic advance in our understanding of what it means to remember.
